Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-22 introduction.tex
Updated table 1, figure 2, and their captions
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1130 ccdd05d5-56c1-461a-bf98-85f6876523b4

\begin{table}[h]
\caption{\label{table:sky-localization-accuracy}Horizon distance, expected detection rate, and \SNR\ at merger for sources that produce an \SNR\ of 8 in all three detectors at time $t$ before merger.  The fifth and sixth columns show the minimum area of the 90\% confidence region before merger and at merger.}
\begin{center}
\begin{tabular}{rrrrrr}
\tableline\tableline
& horiz. & rate & final & \multicolumn{2}{c}{$A$(90\%) (deg$^2$)} \\
\cline{5-6}
$t$ (s) & (Mpc) & (yr$^{-1}$) & \SNR\ & early & final \\
\tableline
25.0 & 226 & 5 & 15.8 & 2893.2 & 1.8 \\
10.0 & 299 & 12 & 11.9 & 1150.6 & 3.6 \\
5.0 & 341 & 18 & 10.4 & 594.6 & 5.1 \\
1.0 & 401 & 29 & 8.9 & 153.9 & 7.5 \\
0.1 & 435 & 37 & 8.2 & 32.5 & 9.1 \\
0.0 & 445 & 40 & 8.0 & 9.6 & 9.6 \\
\tableline
\end{tabular}
\end{center}
\end{table}
%
\begin{figure}[h]
\plotone{figures/loc_in_time.pdf}
\caption{\label{fig:sky-localization-accuracy}Area of the 90\% confidence
region as a function of time for a sources with anticipated detection rates
of 10~yr$^{-1}$, 1~yr$^{-1}$, and 0.1~yr$^{-1}$. The heavy dot indicates the
time at which the accumulated \SNR\ exceeds a threshold of 8.}
\end{figure}

>>>>

\begin{table}[h]
\caption{\label{table:sky-localization-accuracy}Horizon distance, \SNR\ at merger, and area of 90\% confidence at selected times before merger for sources with expected detection rates of 40, 10, 1, and 0.1~yr$^{-1}$.}
\begin{center}
\begin{tabular}{rrrrrrr}
\tableline\tableline
rate & horiz. & final & \multicolumn{4}{c}{$A$(90\%) (deg$^2$)} \\
\cline{4-7}
yr$^{-1}$ & (Mpc) & \SNR\ & 25 s & 10 s & 1 s & 0 s \\
\tableline
40\phd\phn & 445 & 8.0 & 15500 & 3100 & 200 & 9.6 \\
10\phd\phn & 280 & 12.7 & 6100 & 1200 & 78 & 3.8 \\
1\phd\phn & 130 & 27.4 & 1300 & 260 & 17 & 0.8 \\
0.1 & 60 & 58.9 & 280 & 56 & 3.6 & 0.2 \\
\tableline
\end{tabular}
\end{center}
\end{table}
%
\begin{figure}[h]
\plotone{figures/loc_in_time.pdf}
\caption{\label{fig:sky-localization-accuracy}Area of the 90\% confidence
region as a function of time for a sources with anticipated detection rates
of 40, 10, 1, and 0.1~yr$^{-1}$. The heavy dot indicates the
time at which the accumulated \SNR\ exceeds a threshold of 8.}
\end{figure}
